### 2023-01-24 manuscript.tex
overleaf compatibility [ci skip]
This build is based on
https://github.com/stain/2022-fdo-paper/commit/fa45efa5c79f23abe61e9b521cf4269293651d36.

This commit was created by the following CI build and job:
https://github.com/stain/2022-fdo-paper/commit/fa45efa5c79f23abe61e9b521cf4269293651d36/checks
https://github.com/stain/2022-fdo-paper/actions/runs/4001325241

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/64d3fd6d7e3b49d20343cf1a1b33a9e52fb8d9de/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/64d3fd6d7e3b49d20343cf1a1b33a9e52fb8d9de}{stain/2022-fdo-paper@64d3fd6}
on January 24, 2023.

>>>>

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/fa45efa5c79f23abe61e9b521cf4269293651d36/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/fa45efa5c79f23abe61e9b521cf4269293651d36}{stain/2022-fdo-paper@fa45efa}
on January 24, 2023.
